Improving cropland maps through tight integration of human and machine intelligence

### 2020-07-27 inst/manuscript/manuscript.Rmd
Add figures Rmd, manuscript updated through Figure 5

### Model performance
The average performance associated

>>>>

### Model performance
The gain in model performance was assessed for each AOI and for each iteration using a variety of metrics, including overall accuracy, area under the curve of the Receiver Operating Characteristic (AUC), and the F1 score (Figure \ref{fig:alperformance}).

```{r alperformance, echo = FALSE, out.width="100%", fig.cap="Scores for overall Accuracy, area under the curve of the Receiver Operating Characteristic, and the F1 score resulting for the Random Forest model after each iteration of the active learning loop for each AOI (gray lines), as well as the mean score per iteration across all AOIs (black lines).", fig.align='center', message=FALSE}
knitr::include_graphics('figures/figure5.png')
```

The average performance associated
